ICM testing

### 2023-11-20 Scripts/Paper_1.Rmd
Built in a Fecundity-mortality simulation
Now have simulations running.  This is absolutely for sure the final version of the tuning simulations we'll need, until tomorrow.

@@

# Going to remove Sebastes norvegicus because we can't get fecundity as the only data we have is total numbers.
#Stocks <- Stocks[Stocks != "ICES-AFWG_DEEP1-2_Sebastes_norvegicus"]
# Esmarki doesn't work great as it is assessed using a quarterly model.
#Stocks <- Stocks[Stocks != "ICES-WGNSSK_NS 4-3aN_Trisopterus_esmarkii"]
#i = 'ICES-AFWG_NEA1-2_Melanogrammus_aeglefinus'
years.tmp <- NULL
pnm.tmp <- NULL
waa.tmp <- NULL
ages.tmp <- NULL
rem.tmp <- NULL
mx.tmp <- NULL
NE.tmp <- NULL
vpa.tmp <- NULL
am.tmp <- NULL
mr.tmp <- NULL
all.abund.tmp <- NULL
full.abund.tmp <- NULL
for(i in Stocks)
{
  print(i)
  ASR_sub <- ASR_long %>%
    dplyr::select(Year, Stock, type, age, value) %>%
    dplyr::filter(Stock==i)

@@

  age.mat <- data %>% dplyr::select("Year", "age", "AM") %>% pivot_wider(names_from=age, values_from = AM) %>% dplyr::select(-Year)
  prop.nat.mort <- data %>% dplyr::select("Year", "age", "prop.nat.mort") %>% pivot_wider(names_from=age, values_from = prop.nat.mort) %>% dplyr::select(-Year) %>% as.data.frame
  weight.age <- data %>% dplyr::select("Year", "age", "WA") %>% pivot_wider(names_from=age, values_from = WA) %>% dplyr::select(-Year)
  mx <- data %>% dplyr::select("Year", "age", "mx") %>% pivot_wider(names_from=age, values_from = mx) %>% dplyr::select(-Year) %>% as.data.frame()

  # Dealing with some annoying NAs...
  # if(i == "AFSC_BSAI-Males_Pleuronectes_quadrituberculatus")
  # {
  #   age.mat[length(years),] <- age.mat[length(years)-1,]
  #   prop.nat.mort[length(years),] <- prop.nat.mort[length(years)-1,]
  #   weight.age[length(years),] <- weight.age[length(years)-1,]
  #   mx[length(years),13:23] <- mx[length(years),12]
  # }
  # 
  if(i == "DFO_2J3KL_Gadus_morhua")
  {
    age.mat[,10:12] <- 1
    prop.nat.mort[,10:12] <- prop.nat.mort[,9]
    weight.age[12:14,11:12] <- weight.age[12:14,10]
    weight.age[15,12] <- weight.age[15,11]
    mx[12:14,11:12] <- mx[12:14,10]
    mx[15,12] <- mx[15,11]
  }

  if(i == "DFO_4T-Spring_Clupea_harengus")
  {
    age.mat[6:7,12] <- 1
    prop.nat.mort[6:7,12] <- prop.nat.mort[6:7,11]
    weight.age[6:7,12] <- weight.age[6:7,11]
    mx[6:7,12] <- mx[6:7,11]
  }

  if(i == "ICES-HAWG_CS 6a- 7b-7c_Clupea_harengus") 
  {
    age.mat[30,9] <- 1
    prop.nat.mort[30,9] <- prop.nat.mort[30,8]
    weight.age[30,9] <- weight.age[29,9]
    mx[30,9] <- mx[30,8]
  }

  if(i == "ICES-WGCSE_IS6a-7b-7j_Dicentrarchus _labrax")
  {
    age.mat[c(14,27,40),7] <- age.mat[1,7]
    prop.nat.mort[c(14,27,40),7] <- prop.nat.mort[1,7]
    weight.age[c(14,27,40),7] <- weight.age[c(13,26,39),7]
    mx[c(14,27,40),7] <- mx[c(14,27,40),6]
  }
  # Clear out some 0's...
  if( i == "AFSC_EEBSAI_Limanda_aspera")
  {
    mx[4,19] <- mean(unlist(mx[4,c(18,20)]))
    mx[c(5,7),20] <- mx[c(5,7),19]
    mx[1:6,21] <- mx[1:6,20] 
  }
  # For the years of mx without SSB info to inform them
  # if(minage >0 ) 
  # {
  #   mx.fill <- as.data.frame(matrix(rep(colMeans(mx,na.rm=T),minage),nrow=minage,byrow=T),colnames = names(mx))
  #   names(mx) <- names(mx.fill)
  #  # mx <- rbind(mx[(minage+1):nrow(mx),],mx.fill) # or is it
  #   mx <- rbind(mx.fill,mx[(minage+1):nrow(mx),]) # I think this is right!
  # }
  years.tmp[[i]] <- years
  pnm.tmp[[i]] <- prop.nat.mort
  waa.tmp[[i]] <- weight.age
  ages.tmp[[i]] <- minage:maxage
  rem.tmp[[i]] <- rem
  mx.tmp[[i]] <- mx
  NE.tmp[[i]] <- N.end
  vpa.tmp[[i]] <- vpa.abund
  all.abund.tmp[[i]] <- all.abund
  full.abund.tmp[[i]] <- full.abund
  am.tmp[[i]] <- age.mat
  mr.tmp[[i]] <- missing_rem
} #end input data loop

save(years.tmp,pnm.tmp,waa.tmp,ages.tmp,rem.tmp,mx.tmp,NE.tmp,vpa.tmp,mr.tmp,am.tmp,Stocks,ASR_stocks,ASR_long,all.abund.tmp,full.abund.tmp,file =  paste0(loc,"/Results/model_inputs_all_ages.Rdata"))

@@

back.tune.all.res <- NULL
back.tune.summary <- NULL
for.tune.all.res <- NULL
for.tune.summary <- NULL
for(i in Stocks)
{
  years <- years.tmp[[i]]
  prop.nat.mort <- pnm.tmp[[i]] 
  rem <- rem.tmp[[i]] 
  mx <- mx.tmp[[i]] 
  N.end <- NE.tmp[[i]] 
  ages <- ages.tmp[[i]]
  vpa.abund <- vpa.tmp[[i]] 
  all.abund <- all.abund.tmp[[i]]
  #N.end <- vpa.abund[length(vpa.abund)]

   N.start <- all.abund[1]
   print(i)
   # The fecundities are 
   fast.for.tune <- fast.tunes(years,
                           tuner='f',
                           step.size = 0.025, # Make sure n.steps is even please!!
                           abund.ts = all.abund,
                           ages=ages,
                           nm = -(log(1-prop.nat.mort)),
                           rems = rem$rem,
                           fecund = mx,
                           N.init = N.start,
                           direction= 'forwards'
                           )

@@

   fast.back.tune <- fast.tunes(years,
                           tuner='f',
                           step.size = 0.025, # Make sure n.steps is even please!!
                           abund.ts = all.abund,
                           ages = ages,
                           nm = -(log(1-prop.nat.mort)),
                           rems = rem$rem,
                           fecund = mx,
                           N.init = N.end,
                           direction= 'backwards'
                           )

   back.tune.all.res[[i]] <- fast.back.tune
   back.tune.tmp <- data.frame(fast.back.tune$res,Stock = i)
   back.tune.summary[[i]] <- back.tune.tmp

@@

#tst <- do.call('rbind',for.tune.summary)
#quantile(tst$per.diff,probs=seq(0.001,1,0.001),na.rm=T)
# summary(tst$per.diff)
# summary(tst$r)
# tst <- tst[abs(tst$per.diff) > 5,]
# 
# range(tst$per.diff,na.rm=T)
# It completed 33 stocks, was on stock 34
saveRDS(back.tune.summary,"D:/Github/ICM/Results/backwards_fully_tuned_summary.Rds")
saveRDS(for.tune.summary,"D:/Github/ICM/Results/forwards_fully_tuned_summary.Rds")
saveRDS(back.tune.all.res,"D:/Github/ICM/Results/backwards_fully_tuned_all_res.Rds")
saveRDS(for.tune.all.res,"D:/Github/ICM/Results/forwards_fully_tuned_all_res.Rds")

@@

# So we agreed we wanted to look at cod, haddock, herring, and sole using the forward tuning sceanrios...

for.tune.summary <- readRDS("D:/Github/ICM/Results/forwards_fully_tuned_summary.Rds")
for.tune.all <- readRDS("D:/Github/ICM/Results/forwards_fully_tuned_all_res.Rds")

cod <- grep("morhua",names(for.tune.summary))
haddock <- grep('aeglefinus',names(for.tune.summary))
herring <- grep("harengus",names(for.tune.summary))
pollock <- grep("virens",names(for.tune.summary)) 
sole <- grep("solea",names(for.tune.summary))
euro.plaice <- grep("platessa",names(for.tune.summary))
am.plaice <- grep("platessoides",names(for.tune.summary))

p1.stocks <- sort(c(cod,haddock,herring,pollock,sole,euro.plaice,am.plaice))

@@

for.tune.stocks <- NULL
for(i in p1.stocks) 
{
  nam <- Stocks[i]
  #  A quick way to get the other potentially interesting info for the stock...
  meta <- ASR_long[ASR_long$Stock == nam,][1,]
  tmp <- for.tune.summary[[nam]]
  tmp$Management   <- meta$Management  
  tmp$Area <- meta$Area
  tmp$Order <- meta$Order
  tmp$Family   <- meta$Family  
  tmp$Genus  <- meta$Genus 
  tmp$Species <- meta$Species
  tmp$Model <- meta$Model
  tmp$Meeting_or_reference <- meta$Meeting_or_reference
  tmp$Notes <- meta$Notes
  for.tune.stocks[[nam]] <- tmp
}

# Now unpack them...
for.tunes <- do.call("rbind",for.tune.stocks)
# Typo clean up...
for.tunes$Species[for.tunes$Species==" harengus"] <- "harengus"
# Now what does this look like...
paper.stocks <- unique(for.tunes$Stock)

# Now the doubling time simulations for each stock

@@

for(s in 1:100)
{
for(y in 2:100)
{
  r <- sample(na.omit(try$r),size=1)
  pop[y] <- (1+r)*pop[y-1]
} # end the years loop
tmp <- which(pop >= 2*pop[1])[1]

@@

res.fin <- NULL
res.year.fin <- NULL
for(i in paper.stocks)
{
tst <- for.tune.all[[i]]
f.tmp <- tst$fecund.opt
m.tmp <- exp(-tst$nm.opt)
f.org.tmp <- tst$fecund.org
m.org.tmp <- exp(-tst$nm.org)

ages <- 0:(ncol(f.tmp)-1)
n.ages <- length(ages)
years <- tst$res$year
n.years <- length(years)
# Now I need to grab the fecundities and nat morts by cohort
if(n.years > n.ages)
{
res.cohort <- NULL
res.year <- NULL
for(y in 1:(n.years-n.ages+1))
{
  count = 0
  fs <- NA
  lx <- 1
  fs.org <- NA
  lx.org <- 1
  lx.year <- 1
  for(a in 1:n.ages)
  {
  fs[a] <- f.tmp[y+count,a]  
  fs.org[a] <- f.org.tmp[y+count,a]  
  if(a > 1) 
  {
    lx[a] <- lx[a-1] * m.tmp[y+count,a]  
    lx.org[a] <- lx.org[a-1]* m.org.tmp[y+count,a]  
    lx.year[a] <- lx.year[a-1] * m.tmp[y,a]
  }  # end the a > 1 if
  count <- count + 1
  }# end the ages loop
  res.cohort[[y]] <- data.frame(mx.opt = fs,lx.opt = lx,mx.org = fs.org,lx.org = lx.org,age = ages,
                         mx.lx.opt = fs*lx,mx.lx.org = fs.org*lx.org,
                         x.mx.lx.opt = fs*lx*ages,x.mx.lx.org = fs.org*lx.org*ages,
                         cohort=years[y],Stock = i)

  res.year[[y]] <- data.frame(mx.opt = unlist(f.tmp[y,]),lx.opt = lx.year,age = ages,
                         mx.lx.opt = unlist(f.tmp[y,])*lx.year,
                         x.mx.lx.opt = unlist(f.tmp[y,])*lx.year*ages,
                         year=years[y],Stock = i)

@@

for(i in p1.stocks) 
{
  nam <- Stocks[i]
  #  A quick way to get the other potentially interesting info for the stock...
  meta <- ASR_long[ASR_long$Stock == nam,][1,]

  pop.dam$Management[pop.dam$Stock == nam]   <- meta$Management  
  pop.dam$Area[pop.dam$Stock == nam] <- meta$Area
  pop.dam$Order[pop.dam$Stock == nam] <- meta$Order
  pop.dam$Family[pop.dam$Stock == nam]   <- meta$Family  
  pop.dam$Genus[pop.dam$Stock == nam]  <- meta$Genus 
  pop.dam$Species[pop.dam$Stock == nam] <- meta$Species
  pop.dam$Model[pop.dam$Stock == nam] <- meta$Model
  pop.dam$Meeting_or_reference[pop.dam$Stock == nam] <- meta$Meeting_or_reference
  pop.dam$Notes[pop.dam$Stock == nam] <- meta$Notes

@@

pop.dam$Species[pop.dam$Species==" harengus"] <- "harengus"

hmm <- pop.dam %>% dplyr::filter(R0.opt > 500)

hmm

hmm[hmm$Stock == "ICES-WGNSSK_NS  4-6a-20_Melanogrammus_aeglefinus",]
for.tune.all$`ICES-WGNSSK_NS  4-6a-20_Melanogrammus_aeglefinus`$res

unique(hmm$Stock)
# There are 7 stocks with some bat shit happening...
# Fixed... "ICES-WGNSSK_NS4 _Solea_solea"

# These are all problems because the abundance increases like nuts in a few years....
"ICES-AFWG_NEA1-2_Melanogrammus_aeglefinus"
"ICES-WGCSE_CS7e-k_Gadus_morhua"                  
"ICES-WGNSSK_NS  4-6a-20_Melanogrammus_aeglefinus" # Something special weird going on with this stock
"ICES-WGBFAS_WBS-25-32_Gadus_morhua"

# Figure out how to get an r of 10 and what the mx vector needs to look like for
#"ICES-WGNSSK_NS  4-6a-20_Melanogrammus_aeglefinus"

ages <- 0:12 # ages
mx <- c(0.9,500,500,rep(5000,10)) # fecundity
nat.mort <- rep(0.2,13) # natural mortality
si <- 1- nat.mort # survivial

lx <- 1
for(s in 2:(length(si))) lx[s]<-lx[s-1]*si[s-1]

eulerlotka <- function(r) (sum(lx * mx * exp(-r * ages)) - 1)^2

junk<-optimize(lower=-0.999999,upper=55,f = eulerlotka)
res <- c(junk$minimum)
res

p.start <- 10

p.end <- (1+res)*p.start
p.end

R0 <- sum(lx*mx)
R0

tmp <- for.tune.all[["ICES-AFWG_NEA1-2_Melanogrammus_aeglefinus"]]
tmp$nm.org
tmp$fecund.opt
t1 <- vpa.tmp$`ICES-AFWG_NEA1-2_Melanogrammus_aeglefinus`
range(t1[2:length(t1)]/t1[1:(length(t1)-1)])
# So using all the age classes actually reduces the ratios from year to year requiring less insanity...
t2 <- all.abund.tmp$`ICES-AFWG_NEA1-2_Melanogrammus_aeglefinus`
range(t2[2:length(t2)]/t2[1:(length(t2)-1)])

data.frame(tmp$res$year,tmp$res$vpa.abund,t1,t2)

mx <- c(0,0,0,rep(30,11))
nm <- rep(0.2,14)

@@

ggplot(for.tunes) + geom_density(aes(r,group=Species,color=Species,fill=Species),alpha = 0.2)

>>>>

# Something is weird with the mentella stock, I'm going to drop it...
ASR_long <- ASR_long %>% dplyr::filter(Stock != "ICES-AFWG_DEEP1-2_Sebastes_mentella")

@@

# Going to remove Sebastes norvegicus because we can't get fecundity as the only data we have is total numbers.
#Stocks <- Stocks[Stocks != "ICES-AFWG_DEEP1-2_Sebastes_norvegicus"]
# Esmarki doesn't work great as it is assessed using a quarterly model.
#Stocks <- Stocks[Stocks != "ICES-WGNSSK_NS 4-3aN_Trisopterus_esmarkii"]
#i = 'ICES-AFWG_NEA1-2_Melanogrammus_aeglefinus'
years.tmp <- NULL
pnm.tmp <- NULL
waa.tmp <- NULL
ages.tmp <- NULL
rem.tmp <- NULL
mx.tmp <- NULL
NE.tmp <- NULL
vpa.tmp <- NULL
am.tmp <- NULL
mr.tmp <- NULL
all.abund.tmp <- NULL
full.abund.tmp <- NULL
full.rem.tmp <- NULL
fs.tmp <- NULL
for(i in Stocks)
{
  print(i)
  ASR_sub <- ASR_long %>%
    dplyr::select(Year, Stock, type, age, value) %>%
    dplyr::filter(Stock==i)

@@

  age.mat <- data %>% dplyr::select("Year", "age", "AM") %>% pivot_wider(names_from=age, values_from = AM) %>% dplyr::select(-Year)
  prop.nat.mort <- data %>% dplyr::select("Year", "age", "prop.nat.mort") %>% pivot_wider(names_from=age, values_from = prop.nat.mort) %>% dplyr::select(-Year) %>% as.data.frame
  weight.age <- data %>% dplyr::select("Year", "age", "WA") %>% pivot_wider(names_from=age, values_from = WA) %>% dplyr::select(-Year)
  mx <- data %>% dplyr::select("Year", "age", "mx") %>% pivot_wider(names_from=age, values_from = mx) %>% dplyr::select(-Year) %>% as.data.frame()
  abund.age <- data %>% dplyr::select("Year", "age", "Num") %>% pivot_wider(names_from=age, values_from = Num) %>% dplyr::select(-Year) %>% as.data.frame()
  # Now we can save out the catch and get an instantaneous F
  data$Catch[is.na(data$Catch)] <- 0
  data$Exp <- data$Catch/data$Num
  # If it is exactly 1 that leads to an Inf, which is annoying, so make it 1.1 and fix it with the rest below
  data$Exp[data$Exp == 1] <- 1.1
  # And make this an F
  data$Fs <- -log(1-data$Exp)
  if(any(is.na(data$Fs)))
  {
    fixers <- which(is.na(data$Fs))
    print(paste0("Had to replace ",length(fixers), ' exploitation rates for stock ',i))
    for(f in fixers)
    {
      yr <- data$Year[f]
      fs <- max(data$Fs[data$Year == yr],na.rm=T)
      data$Fs[f] <- fs
      data$Exp[f] <- 1-exp(-fs)
    }
  }

  full.rems <- data %>% dplyr::select("Year", "age", "Catch") %>% pivot_wider(names_from=age, values_from = Catch) %>% dplyr::select(-Year)
  full.Fs <-  data %>% dplyr::select("Year", "age", "Fs") %>% pivot_wider(names_from=age, values_from = Fs) %>% dplyr::select(-Year)

  if(i == "DFO_2J3KL_Gadus_morhua")
  {
    age.mat[,10:12] <- 1
    prop.nat.mort[,10:12] <- prop.nat.mort[,9]
    weight.age[12:14,11:12] <- weight.age[12:14,10]
    weight.age[15,12] <- weight.age[15,11]
    mx[12:14,11:12] <- mx[12:14,10]
    mx[15,12] <- mx[15,11]
    full.Fs[12:14,11:12] <- full.Fs[12:14,10]
    full.Fs[15,12] <- full.Fs[15,11]
    abund.age[12:14,11:12] <- abund.age[12:14,10]
    abund.age[15,12] <- abund.age[15,11]
    # I could calculate, but this will get us to the same place...
    full.rems[12:14,11:12] <- full.rems[12:14,10]
    full.rems[15,12] <- full.rems[15,11]
  }

  if(i == "DFO_4T-Spring_Clupea_harengus")
  {
    age.mat[6:7,12] <- 1
    prop.nat.mort[6:7,12] <- prop.nat.mort[6:7,11]
    weight.age[6:7,12] <- weight.age[6:7,11]
    mx[6:7,12] <- mx[6:7,11]
    full.Fs[6:7,12] <- full.Fs[6:7,11]
    abund.age[6:7,12] <- abund.age[6:7,11]
    full.rems[6:7,12] <- full.rems[6:7,11]
  }

  if(i == "ICES-HAWG_CS 6a- 7b-7c_Clupea_harengus") 
  {
    age.mat[30,9] <- 1
    prop.nat.mort[30,9] <- prop.nat.mort[30,8]
    weight.age[30,9] <- weight.age[29,9]
    mx[30,9] <- mx[30,8]
    full.Fs[30,9] <- full.Fs[30,8]
    abund.age[30,9] <- abund.age[30,8]
    full.rems[30,9] <- full.rems[30,8]
  }

  if(i == "ICES-WGCSE_IS6a-7b-7j_Dicentrarchus _labrax")
  {
    age.mat[c(14,27,40),7] <- age.mat[1,7]
    prop.nat.mort[c(14,27,40),7] <- prop.nat.mort[1,7]
    weight.age[c(14,27,40),7] <- weight.age[c(13,26,39),7]
    mx[c(14,27,40),7] <- mx[c(14,27,40),6]
    full.Fs[c(14,27,40),7] <- full.Fs[c(14,27,40),6]
    abund.age[c(14,27,40),7] <- abund.age[c(14,27,40),6]
    full.rems[c(14,27,40),7] <- full.rems[c(14,27,40),6]
  }
  # Clear out some 0's...
  if( i == "AFSC_EEBSAI_Limanda_aspera")
  {
    mx[4,19] <- mean(unlist(mx[4,c(18,20)]))
    mx[c(5,7),20] <- mx[c(5,7),19]
    mx[1:6,21] <- mx[1:6,20] 
  }
  # For the years of mx without SSB info to inform them
  # if(minage >0 ) 
  # {
  #   mx.fill <- as.data.frame(matrix(rep(colMeans(mx,na.rm=T),minage),nrow=minage,byrow=T),colnames = names(mx))
  #   names(mx) <- names(mx.fill)
  #  # mx <- rbind(mx[(minage+1):nrow(mx),],mx.fill) # or is it
  #   mx <- rbind(mx.fill,mx[(minage+1):nrow(mx),]) # I think this is right!
  # }
  years.tmp[[i]] <- years
  pnm.tmp[[i]] <- prop.nat.mort
  waa.tmp[[i]] <- weight.age
  ages.tmp[[i]] <- minage:maxage
  rem.tmp[[i]] <- rem
  mx.tmp[[i]] <- mx
  NE.tmp[[i]] <- N.end
  vpa.tmp[[i]] <- vpa.abund
  all.abund.tmp[[i]] <- all.abund
  full.abund.tmp[[i]] <- abund.age
  am.tmp[[i]] <- age.mat
  mr.tmp[[i]] <- missing_rem
  fs.tmp[[i]] <- full.Fs
  full.rem.tmp[[i]] <- full.rems
} #end input data loop

save(years.tmp,pnm.tmp,waa.tmp,ages.tmp,rem.tmp,mx.tmp,NE.tmp,vpa.tmp,mr.tmp,am.tmp,Stocks,ASR_stocks,ASR_long,all.abund.tmp,full.abund.tmp,fs.tmp,full.rem.tmp,file =  paste0(loc,"/Results/model_inputs_all_ages.Rdata"))

@@

back.tune.all.res <- NULL
back.tune.summary <- NULL
for.tune.all.res <- NULL
for.tune.summary <- NULL
for(i in Stocks)
{
  years <- years.tmp[[i]]
  prop.nat.mort <- pnm.tmp[[i]] 
  #rem <- rem.tmp[[i]] 
  mx <- mx.tmp[[i]] 
  N.end <- NE.tmp[[i]] 
  ages <- ages.tmp[[i]]
  vpa.abund <- vpa.tmp[[i]] 
  all.abund <- all.abund.tmp[[i]]
  fs <-fs.tmp[[i]]
  full.rem <- full.rem.tmp[[i]]
  full.abund <- full.abund.tmp[[i]]
  #all.abund <- full.abund.tmp[[i]]
  #N.end <- vpa.abund[length(vpa.abund)]
  #Pick your step size
  ss.size <- 0.01
  sensistive.stocks <- c("ICES-WGNSSK_NS 4-3aN_Trisopterus_esmarkii",
                          "ICES-HAWG_NS_Ammodytes_dubius",
                          "DFO_2J3KL_Gadus_morhua",
                          "DFO_3Pn-4RS_Gadus_morhua",
                          "DFO_4T-4VN_Gadus_morhua",
                          "ICES-WGCSE_IS7a_Gadus_morhua",
                          "ICES-WGCSE_CS7a_Merlangius_merlangus",
                          "ICES-WGNSSK_NS 4-7d,20_Gadus_morhua",
                          "ICES-WGNSSK_NS  4-6a-20_Melanogrammus_aeglefinus",
                          "ICES-WGHANSA_SP8abd_Sardina _pilchardus",
                          "ICES-WGNSSK_NS 4-7d_Merlangius_merlangus",
                          "NEFSC-GARMIII_SNE- MA_Limanda_ferruginea",
                          "NEFSC-GARMIII_MA_Paralichthys_dentatus",
                          "ICES-WGCSE_CS7e-k_Gadus_morhua",
                          "DFO_4T_Scomber_scombrus",
                          "ICES-WGCSE_CS27.6a_Merlangius_merlangus",
                          "ICES-WGBFAS_BS 22-32_Sprattus_sprattus",
                           "AFSC_GOA_Theragra_chalcogramma")

  if(i %in% sensistive.stocks) ss.size = ss.size/10

   N.start <- all.abund[1]
   print(i)
   # The fecundities are 
   fast.for.tune <- fast.tunes(years,
                           tuner='fec_nm',
                           step.size = ss.size, 
                           abund.ts = all.abund,
                           ages=ages,
                           nm = -(log(1-prop.nat.mort)),
                           fecund = mx,
                           fm = fs,
                           abund.age = full.abund, 
                           catch.age = full.rem, 
                           N.init = N.start,
                           direction= 'forwards'
                           )

@@

   # fast.back.tune <- fast.tunes(years,
   #                         tuner='fm',
   #                         step.size = 0.01, # Make sure n.steps is even please!!
   #                         abund.ts = all.abund,
   #                         ages=ages,
   #                         nm = -(log(1-prop.nat.mort)),
   #                         fecund = mx,
   #                         fm = fs,
   #                         abund.age = full.abund, 
   #                         catch.age = full.rem, 
   #                         N.init = N.end,
   #                         direction= 'backwards'
   #                         )
   # 
   # back.tune.all.res[[i]] <- fast.back.tune
   # back.tune.tmp <- data.frame(fast.back.tune$res,Stock = i)
   # back.tune.summary[[i]] <- back.tune.tmp

@@

#DFO_2J3KL_Gadus_morhua -27.7984654 2.815738e+08
#ICES-WGCSE_IS6a-7b-7j_Dicentrarchus _labrax -21.6050608
# ICES-WGCSE_IS6a-7b-7j_Dicentrarchus _labrax Lotka error
# ICES-HAWG_CS 6a- 7b-7c_Clupea_harengus # lotka error

# Fixed...
#ICES-HAWG_NS_Ammodytes_dubius Overshoot
# ICES-WGNSSK_NS 4-3aN_Trisopterus_esmarkii  Overshoot
#ICES-WGNSSK_NS 4-7d,20_Gadus_morhua Overshoot
# ICES-WGNSSK_NS  4-6a-20_Melanogrammus_aeglefinus Overshoot
# ICES-WGCSE_ISbc-ek_Melanogrammus_aeglefinus  Overshoot

#saveRDS(for.tune.summary,"D:/Github/ICM/Results/forwards_fully_tuned_summary_z.Rds")
#saveRDS(for.tune.all.res,"D:/Github/ICM/Results/forwards_fully_tuned_all_res_z.Rds")
# saveRDS(for.tune.summary,"D:/Github/ICM/Results/forwards_fully_tuned_summary_nm.Rds")
# saveRDS(for.tune.all.res,"D:/Github/ICM/Results/forwards_fully_tuned_all_res_nm.Rds")
#saveRDS(for.tune.summary,"D:/Github/ICM/Results/forwards_fully_tuned_summary_fm.Rds")
#saveRDS(for.tune.all.res,"D:/Github/ICM/Results/forwards_fully_tuned_all_res_fm.Rds")
saveRDS(for.tune.summary,"D:/Github/ICM/Results/forwards_fully_tuned_summary_fec_nm.Rds")
saveRDS(for.tune.all.res,"D:/Github/ICM/Results/forwards_fully_tuned_all_res_fec_nm.Rds")
#

@@

# We are now looking at everything, lifetime reproductive success

for.tune.summary <- readRDS("D:/Github/ICM/Results/forwards_fully_tuned_summary_fec_nm.Rds")
for.tune.all <- readRDS("D:/Github/ICM/Results/forwards_fully_tuned_all_res_fec_nm.Rds")

# 
# cod <- grep("morhua",names(for.tune.summary))
# haddock <- grep('aeglefinus',names(for.tune.summary))
# herring <- grep("harengus",names(for.tune.summary))
# pollock <- grep("virens",names(for.tune.summary)) 
# sole <- grep("solea",names(for.tune.summary))
# euro.plaice <- grep("platessa",names(for.tune.summary))
# am.plaice <- grep("platessoides",names(for.tune.summary))
# 
# p1.stocks <- sort(c(cod,haddock,herring,pollock,sole,euro.plaice,am.plaice))

@@

for.tune.stocks <- NULL
for(i in 1:n.stocks) 
{
  nam <- Stocks[i]
  #  A quick way to get the other potentially interesting info for the stock...
  meta <- ASR_long[ASR_long$Stock == nam,][1,]
  tmp <- for.tune.summary[[nam]]
  tmp$Management   <- meta$Management  
  tmp$Area <- meta$Area
  if(nam == "NEFSC-GARMIII_GB_Gadus_morhua") tmp$Area <- "GB (West)"
  tmp$Order <- meta$Order
  tmp$Family   <- meta$Family  
  tmp$Genus  <- meta$Genus 
  tmp$Species <- meta$Species
  tmp$Model <- meta$Model
  tmp$Meeting_or_reference <- meta$Meeting_or_reference
  tmp$Notes <- meta$Notes
  #tmp$removals.init <- rem.tmp[[nam]]$rem
  for.tune.stocks[[nam]] <- tmp
}

# Now unpack them...
for.tunes <- do.call("rbind",for.tune.stocks)
# Typo clean up...
for.tunes$Species[for.tunes$Species==" harengus"] <- "harengus"
for.tunes$Species[for.tunes$Species=="Aeglefinus"] <- "aeglefinus"
for.tunes$Species[for.tunes$Species=="Solea"] <- "solea"

# What Stocks suck
# sucker.check <- for.tunes %>% dplyr::group_by(Stock) %>% dplyr::summarise(min = min(per.diff,na.rm=T),
#                                                                           max = max(per.diff,na.rm=T))
# View(sucker.check)
# 
# # FM issues are all really related to having very low fishing mortality years...
# # Not really sure how to handle that... maybe an if in the code to make a big jump if model is nowhere on convergence
# # and fishing is < 10% of mean F for the population, that would cover all the problems I'm seeing here.
# # Has years with 0 fishing, need to put in something
# "ICES-WGNSSK_NS4 _Scopthalmus_maximus"
# "ICES-WGNSSK_NS 4-3aN_Trisopterus_esmarkii"
# # Removals so low the step size isn't enough...
# "DFO_3Pn-4RS_Gadus_morhua" # Worked great until the second last year then it did nothing, I think the step size was too small
# "DFO_4T-4VN_Gadus_morhua" # In 1995 it just does nothing, I think because the step size is too small due to super low F.
# "DFO_4T_Hippoglossoides _platessoides"
# "NEFSC-GARMIII_GOM-CHATT_Morone_saxatilis"
# tst <- for.tunes %>% dplyr::filter(Stock == "ICES-HAWG_NS_Ammodytes_dubius")
# 
# # Now what does this look like...
# paper.stocks <- unique(for.tunes$Stock)
# 
# tst <- for.tunes %>% dplyr::group_by(Stock) %>% dplyr::summarise(min = min(per.diff,na.rm=T),
#                                                                  max = max(per.diff, na.rm=T))
# # Now the doubling time simulations for each stock

@@

for(s in 1:100)
{
for(y in 2:100)
{
  lambda <- sample(na.omit(try$lambda),size=1)
  pop[y] <- lambda*pop[y-1]
} # end the years loop
tmp <- which(pop >= 2*pop[1])[1]

@@

res.fin <- NULL
res.year.fin <- NULL
for(i in paper.stocks)
{
  tst <- for.tune.all[[i]]
  # Fishing mortality
  fm.org.tmp <- fs.tmp[[i]]
  fm.tmp <- tst$fm.opt
  # fecundity
  fec.tmp <- tst$fecund.opt
  fec.org.tmp <- tst$fecund.org
  # Natural mortality
  m.org.tmp <- exp(-tst$nm.org)
  m.tmp <- exp(-tst$nm.opt)
  # Total mortality
  z.tmp <- exp(-tst$z.opt)
  z.org.tmp <- exp(-tst$nm.org -fm.org.tmp)

  ages <- 0:(ncol(fec.tmp)-1)
  n.ages <- length(ages)
  years <- tst$res$year
  n.years <- length(years)
  # Now I need to grab the fecundities and nat morts by cohort
  if(n.years > n.ages)
  {
  res.cohort <- NULL
  res.year <- NULL
  for(y in 1:(n.years-n.ages+1))
  {
    count = 0
    fs <- NA
    lx <- 1
    fs.org <- NA
    lx.org <- 1
    lx.year <- 1
    for(a in 1:n.ages)
    {
    fs[a] <- fec.tmp[y+count,a]  
    fs.org[a] <- fec.org.tmp[y+count,a]  
    if(a > 1) 
    {
      lx[a] <- lx[a-1] * m.tmp[y+count,a]  
      lx.org[a] <- lx.org[a-1]* m.org.tmp[y+count,a]  
      lx.year[a] <- lx.year[a-1] * m.tmp[y,a]
    }  # end the a > 1 if
    count <- count + 1
    }# end the ages loop
    res.cohort[[y]] <- data.frame(mx.opt = fs,lx.opt = lx,mx.org = fs.org,lx.org = lx.org,age = ages,
                           mx.lx.opt = fs*lx,mx.lx.org = fs.org*lx.org,
                           x.mx.lx.opt = fs*lx*ages,x.mx.lx.org = fs.org*lx.org*ages,
                           cohort=years[y],Stock = i)

    res.year[[y]] <- data.frame(mx.opt = unlist(fec.tmp[y,]),lx.opt = lx.year,age = ages,
                           mx.lx.opt = unlist(fec.tmp[y,])*lx.year,
                           x.mx.lx.opt = unlist(fec.tmp[y,])*lx.year*ages,
                           year=years[y],Stock = i)

@@

for(i in 1:n.stocks) 
{
  nam <- Stocks[i]
  #  A quick way to get the other potentially interesting info for the stock...
  meta <- ASR_long[ASR_long$Stock == nam,][1,]

  pop.dam$Management[pop.dam$Stock == nam]   <- meta$Management  
  pop.dam$Area[pop.dam$Stock == nam] <- meta$Area
  if(nam == "NEFSC-GARMIII_GB_Gadus_morhua") pop.dam$Area[pop.dam$Stock == nam] <- "GB (West)"
  pop.dam$Order[pop.dam$Stock == nam] <- meta$Order
  pop.dam$Family[pop.dam$Stock == nam]   <- meta$Family  
  pop.dam$Genus[pop.dam$Stock == nam]  <- meta$Genus 
  pop.dam$Species[pop.dam$Stock == nam] <- meta$Species
  pop.dam$Model[pop.dam$Stock == nam] <- meta$Model
  pop.dam$Meeting_or_reference[pop.dam$Stock == nam] <- meta$Meeting_or_reference
  pop.dam$Notes[pop.dam$Stock == nam] <- meta$Notes

@@

pop.dam$Species[pop.dam$Species==" harengus"] <- "harengus"
pop.dam$Species[pop.dam$Species=="Aeglefinus"] <- "aeglefinus"
pop.dam$Species[pop.dam$Species=="Solea"] <- "solea"

@@

ggplot(for.tunes) + geom_density(aes(lambda,group=Species,color=Species,fill=Species),alpha = 0.2) + scale_x_continuous(breaks = c(0,0.5,1,2,5,10))
